Capstone Movielens Report

### 2025-05-06 reports/capstone-movielens-report.draft4.tex
Draft RMD report updated.

\title{Capstone Movielens Report}
\author{Azamat Kurbanaev}
\date{2025-05-05}

@@

@@

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-22-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-23-1.pdf}

@@

We will split the \texttt{edx} dataset into a training set, which we
will use to build and train our models, and a test set in which we will
compute the accuracy of our predictions, the way described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
23.1.1 Movielens data} of the \emph{Course Textbook} mentioned
above\autocite{IDS2_23-1-1}.We will also use the \emph{5-Fold Cross
Validation} method the way described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html\#cross-validation}{Section
29.6 Cross validation} of the \emph{Course Textbook}. To prepare
datasets for processing, we will use the following functions,
specifically designed for these operations:

@@

\begin{itemize}
\tightlist
\item
  \texttt{make\_source\_datasets};
\item
  \texttt{init\_source\_datasets}.
\end{itemize}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{y }\OtherTok{\textless{}{-}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(train\_set, movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
\FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
\FunctionTok{column\_to\_rownames}\NormalTok{(}\StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
\FunctionTok{as.matrix}\NormalTok{()}

\FunctionTok{dim}\NormalTok{(y)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 24115 10630
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{movie\_map }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}}\NormalTok{ dplyr}\SpecialCharTok{::}\FunctionTok{select}\NormalTok{(movieId, title, genres) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{distinct}\NormalTok{(movieId, }\AttributeTok{.keep\_all =} \ConstantTok{TRUE}\NormalTok{)}

\FunctionTok{summary}\NormalTok{(movie\_map)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##     movieId         title              genres         
##  1      :    1   Length:10630       Length:10630      
##  2      :    1   Class :character   Class :character  
##  3      :    1   Mode  :character   Mode  :character  
##  4      :    1                                        
##  5      :    1                                        
##  6      :    1                                        
##  (Other):10624
\end{verbatim}

@@

\subsubsection{Naive Model}\label{naive-model}

\hfill\break
Let's begin our analysis by evaluating the simplest model described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#a-first-model}{Section
\emph{23.3 The First Model} of the \emph{Course Textbook}}, and then
gradually refine it through further research. It is about a model that
assumes the same rating for all movies and users with all the
differences explained by random variation would look as follows:

>>>>

\title{Capstone Movielens Report}
\author{Azamat Kurbanaev}
\date{2025-05-06}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-11-1.pdf}

@@

\includegraphics{capstone-movielens-report.draft4_files/figure-latex/unnamed-chunk-14-1.pdf}

@@

@@

@@

We will split the \texttt{edx} dataset into a training set, which we
will use to build and train our models, and a test set in which we will
compute the accuracy of our predictions, the way described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html\#movielens-data}{Section
23.1.1 Movielens data} of the \emph{Course Textbook} mentioned
above\autocite{IDS2_23-1-1}.We will also use the \emph{5-Fold Cross
Validation} method as described in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html\#cross-validation}{Section
29.6 Cross validation} of the \emph{Course Textbook}. To prepare
datasets for processing, we will use the following functions,
specifically designed for these operations:

@@

@@

\paragraph{\texorpdfstring{The \texttt{make\_source\_datasets}
function}{The make\_source\_datasets function}}\label{the-make_source_datasets-function}

Let's take a closer look at the objects we will receive as a result of
executing this function.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{make\_source\_datasets }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{()\{}
  \CommentTok{\# ...}
  \FunctionTok{list}\NormalTok{(}\AttributeTok{edx\_CV =}\NormalTok{ edx\_CV,}
       \AttributeTok{edx.mx =}\NormalTok{ edx.mx,}
       \AttributeTok{edx.sgr =}\NormalTok{ edx.sgr,}
       \AttributeTok{tuning\_sets =}\NormalTok{ tuning\_sets,}
       \AttributeTok{movie\_map =}\NormalTok{ movie\_map,}
       \AttributeTok{date\_days\_map =}\NormalTok{ date\_days\_map)}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\subparagraph{\texorpdfstring{\texttt{edx.mx} Matrix
Object}{edx.mx Matrix Object}}\label{edx.mx-matrix-object}

@@

\begin{Shaded}
\begin{Highlighting}[]
  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Creating Rating Matrix from \textasciigrave{}edx\textasciigrave{} dataset..."}\NormalTok{)}
\NormalTok{  edx.mx }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId),}
           \AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{select}\NormalTok{(movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{column\_to\_rownames}\NormalTok{(}\StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{as.matrix}\NormalTok{()}

  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}:}
\StringTok{Matrix created: \textasciigrave{}edx.mx\textasciigrave{} of the following dimentions:"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
  \FunctionTok{str}\NormalTok{(edx.mx)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##  num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
##  - attr(*, "dimnames")=List of 2
##   ..$ : chr [1:69878] "1" "2" "3" "4" ...
##   ..$ : chr [1:10677] "122" "185" "292" "316" ...
\end{verbatim}

\subparagraph{\texorpdfstring{\texttt{edx.sgr}
Object}{edx.sgr Object}}\label{edx.sgr-object}

To account for the Movie Genre Effect more accurately, we need a dataset
with split rows for movies belonging to multiple genres:

\begin{Shaded}
\begin{Highlighting}[]
  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
\StringTok{To account for the Movie Genre Effect, we need a dataset with split rows }
\StringTok{for movies belonging to multiple genres."}\NormalTok{)}
\NormalTok{  edx.sgr }\OtherTok{\textless{}{-}} \FunctionTok{splitGenreRows}\NormalTok{(edx)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{str}\NormalTok{(edx.sgr)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## tibble [23,371,423 x 6] (S3: tbl_df/tbl/data.frame)
##  $ userId   : int [1:23371423] 1 1 1 1 1 1 1 1 1 1 ...
##  $ movieId  : int [1:23371423] 122 122 185 185 185 292 292 292 292 316 ...
##  $ rating   : num [1:23371423] 5 5 5 5 5 5 5 5 5 5 ...
##  $ timestamp: int [1:23371423] 838985046 838985046 838983525 838983525 838983525 838983421 838983421 838983421 838983421 838983392 ...
##  $ title    : chr [1:23371423] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
##  $ genres   : chr [1:23371423] "Comedy" "Romance" "Action" "Crime" ...
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(edx.sgr)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      userId         movieId          rating        timestamp            title              genres         
##  Min.   :    1   Min.   :    1   Min.   :0.500   Min.   :7.897e+08   Length:23371423    Length:23371423   
##  1st Qu.:18140   1st Qu.:  616   1st Qu.:3.000   1st Qu.:9.472e+08   Class :character   Class :character  
##  Median :35784   Median : 1748   Median :4.000   Median :1.042e+09   Mode  :character   Mode  :character  
##  Mean   :35886   Mean   : 4277   Mean   :3.527   Mean   :1.035e+09                                        
##  3rd Qu.:53638   3rd Qu.: 3635   3rd Qu.:4.000   3rd Qu.:1.131e+09                                        
##  Max.   :71567   Max.   :65133   Max.   :5.000   Max.   :1.231e+09
\end{verbatim}

Note that we use the \texttt{splitGenreRows} function to split rows of
the original dataset:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{splitGenreRows }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(data)\{}
  \FunctionTok{put}\NormalTok{(}\StringTok{"Splitting dataset rows related to multiple genres..."}\NormalTok{)}
\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
\NormalTok{  gs\_splitted }\OtherTok{\textless{}{-}}\NormalTok{ data }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{separate\_rows}\NormalTok{(genres, }\AttributeTok{sep =} \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{|"}\NormalTok{)}
  \FunctionTok{put}\NormalTok{(}\StringTok{"Dataset rows related to multiple genres have been splitted to have single genre per row."}\NormalTok{)}
  \FunctionTok{put\_end\_date}\NormalTok{(start)}
\NormalTok{  gs\_splitted}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{noteblock}
The source code of the function mentioned above is also available in the
\href{https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/2c5d96ac98a8b8fa4151aa8295f91ac29d9472b3/r/src/support-functions/data.helper.functions.R\#L86}{\texttt{Initialize\ input\ datasets}
section of the \texttt{data.helper.functions.R} script on \emph{GitHub}}

\subparagraph{\texorpdfstring{\texttt{movie\_map}
Object}{movie\_map Object}}\label{movie_map-object}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{movie\_map }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}} \FunctionTok{select}\NormalTok{(movieId, title, genres) }\SpecialCharTok{|\textgreater{}} 
    \FunctionTok{distinct}\NormalTok{(movieId, }\AttributeTok{.keep\_all =} \ConstantTok{TRUE}\NormalTok{)}

  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Dataset created: movie\_map"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{str}\NormalTok{(movie\_map)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 'data.frame':    10677 obs. of  3 variables:
##  $ movieId: int  122 185 292 316 329 355 356 362 364 370 ...
##  $ title  : chr  "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
##  $ genres : chr  "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(movie\_map)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##     movieId         title              genres         
##  Min.   :    1   Length:10677       Length:10677      
##  1st Qu.: 2754   Class :character   Class :character  
##  Median : 5434   Mode  :character   Mode  :character  
##  Mean   :13105                                        
##  3rd Qu.: 8710                                        
##  Max.   :65133
\end{verbatim}

@@

\subparagraph{\texorpdfstring{\texttt{date\_days\_map}
Object}{date\_days\_map Object}}\label{date_days_map-object}

We have a \texttt{timestamp} field in the \texttt{edx} dataset. To be
able to map the date, year, and number of days since the earliest record
in the \texttt{edx} dataset with the corresponding value in this field,
we create the following lookup table:

\begin{Shaded}
\begin{Highlighting}[]
  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Creating Date{-}Days Map dataset..."}\NormalTok{)}
\NormalTok{  date\_days\_map }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_time =} \FunctionTok{as\_datetime}\NormalTok{(timestamp)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date =} \FunctionTok{as\_date}\NormalTok{(date\_time)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{year =} \FunctionTok{year}\NormalTok{(date\_time)) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{days =} \FunctionTok{as.integer}\NormalTok{(date }\SpecialCharTok{{-}} \FunctionTok{min}\NormalTok{(date))) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{select}\NormalTok{(timestamp, date\_time, date, year, days) }\SpecialCharTok{|\textgreater{}}
    \FunctionTok{distinct}\NormalTok{(timestamp, }\AttributeTok{.keep\_all =} \ConstantTok{TRUE}\NormalTok{)}

  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Dataset created: date\_days\_map"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
  \FunctionTok{str}\NormalTok{(date\_days\_map)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 'data.frame':    6519590 obs. of  5 variables:
##  $ timestamp: int  838985046 838983525 838983421 838983392 838984474 838983653 838984885 838983707 838984596 838983834 ...
##  $ date_time: POSIXct, format: "1996-08-02 11:24:06" "1996-08-02 10:58:45" "1996-08-02 10:57:01" "1996-08-02 10:56:32" ...
##  $ date     : Date, format: "1996-08-02" "1996-08-02" "1996-08-02" "1996-08-02" ...
##  $ year     : num  1996 1996 1996 1996 1996 ...
##  $ days     : int  571 571 571 571 571 571 571 571 571 571 ...
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
  \FunctionTok{summary}\NormalTok{(date\_days\_map)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##    timestamp           date_time                           date                 year           days     
##  Min.   :7.897e+08   Min.   :1995-01-09 11:46:49.00   Min.   :1995-01-09   Min.   :1995   Min.   :   0  
##  1st Qu.:9.783e+08   1st Qu.:2001-01-01 05:05:01.75   1st Qu.:2001-01-01   1st Qu.:2001   1st Qu.:2184  
##  Median :1.091e+09   Median :2004-08-03 01:08:18.50   Median :2004-08-03   Median :2004   Median :3494  
##  Mean   :1.066e+09   Mean   :2003-10-10 23:15:02.07   Mean   :2003-10-10   Mean   :2003   Mean   :3196  
##  3rd Qu.:1.152e+09   3rd Qu.:2006-07-04 20:41:57.50   3rd Qu.:2006-07-04   3rd Qu.:2006   3rd Qu.:4194  
##  Max.   :1.231e+09   Max.   :2009-01-05 05:02:16.00   Max.   :2009-01-05   Max.   :2009   Max.   :5110
\end{verbatim}

\subparagraph{\texorpdfstring{\texttt{edx\_CV}
Object}{edx\_CV Object}}\label{edx_cv-object}

Here we have a list of sample objects we need to perform the
\emph{5-Fold Cross Validation} as explained in
\href{https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html\#k-fold-cross-validation}{Section
29.6.1 K-fold cross validation} of the \emph{Course Textbook}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{  start }\OtherTok{\textless{}{-}} \FunctionTok{put\_start\_date}\NormalTok{()}
\NormalTok{  edx\_CV }\OtherTok{\textless{}{-}} \FunctionTok{lapply}\NormalTok{(kfold\_index,  }\ControlFlowTok{function}\NormalTok{(fold\_i)\{}

    \FunctionTok{put\_log1}\NormalTok{(}\StringTok{"Method \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
\StringTok{Creating K{-}Fold Cross Validation Datasets, Fold \%1"}\NormalTok{, fold\_i)}

    \CommentTok{\#\textgreater{} We split the initial datasets into training sets, which we will use to build }
    \CommentTok{\#\textgreater{} and train our models, and validation sets in which we will compute the accuracy }
    \CommentTok{\#\textgreater{} of our predictions, the way described in the \textasciigrave{}Section 23.1.1 Movielens data\textasciigrave{}}
    \CommentTok{\#\textgreater{} (https://rafalab.dfci.harvard.edu/dsbook{-}part{-}2/highdim/regularization.html\#movielens{-}data) }
    \CommentTok{\#\textgreater{} of the Course Textbook.}

\NormalTok{    split\_sets }\OtherTok{\textless{}{-}}\NormalTok{ edx }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{sample\_train\_validation\_sets}\NormalTok{(fold\_i}\SpecialCharTok{*}\DecValTok{1000}\NormalTok{)}

\NormalTok{    train\_set }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets}\SpecialCharTok{$}\NormalTok{train\_set}
\NormalTok{    validation\_set }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets}\SpecialCharTok{$}\NormalTok{validation\_set}

    \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
\StringTok{Sampling 20\% from the split{-}row version of the \textasciigrave{}edx\textasciigrave{} dataset..."}\NormalTok{)}
\NormalTok{    split\_sets.gs }\OtherTok{\textless{}{-}}\NormalTok{ edx.sgr }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{sample\_train\_validation\_sets}\NormalTok{(fold\_i}\SpecialCharTok{*}\DecValTok{2000}\NormalTok{)}

\NormalTok{    train.sgr }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets.gs}\SpecialCharTok{$}\NormalTok{train\_set}
\NormalTok{    validation.sgr }\OtherTok{\textless{}{-}}\NormalTok{ split\_sets.gs}\SpecialCharTok{$}\NormalTok{validation\_set}

    \CommentTok{\# put\_log("Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Dataset created: validation.sgr")}
    \CommentTok{\# put(summary(validation.sgr))}

    \CommentTok{\#\textgreater{} We will use the array representation described in \textasciigrave{}Section 17.5 of the Textbook\textasciigrave{}}
    \CommentTok{\#\textgreater{} (https://rafalab.dfci.harvard.edu/dsbook{-}part{-}2/linear{-}models/treatment{-}effect{-}models.html\#sec{-}anova), }
    \CommentTok{\#\textgreater{} for the training data. }
    \CommentTok{\#\textgreater{} To create this matrix, we use \textasciigrave{}tidyr::pivot\_wider\textasciigrave{} function:}

    \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: Creating Rating Matrix from Train Set..."}\NormalTok{)}
\NormalTok{    train\_mx }\OtherTok{\textless{}{-}}\NormalTok{ train\_set }\SpecialCharTok{|\textgreater{}} 
      \FunctionTok{mutate}\NormalTok{(}\AttributeTok{userId =} \FunctionTok{factor}\NormalTok{(userId),}
             \AttributeTok{movieId =} \FunctionTok{factor}\NormalTok{(movieId)) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{select}\NormalTok{(movieId, userId, rating) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ movieId, }\AttributeTok{values\_from =}\NormalTok{ rating) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{column\_to\_rownames}\NormalTok{(}\StringTok{"userId"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
      \FunctionTok{as.matrix}\NormalTok{()}

    \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}:}
\StringTok{Matrix created: \textasciigrave{}train\_mx\textasciigrave{} of the following dimentions:"}\NormalTok{)}
    \FunctionTok{put}\NormalTok{(}\FunctionTok{dim}\NormalTok{(train\_mx))}

    \FunctionTok{list}\NormalTok{(}\AttributeTok{train\_set =}\NormalTok{ train\_set,}
         \AttributeTok{train\_mx =}\NormalTok{ train\_mx,}
         \AttributeTok{train.sgr =}\NormalTok{ train.sgr,}
         \AttributeTok{validation\_set =}\NormalTok{ validation\_set)}
\NormalTok{  \})}
  \FunctionTok{put\_end\_date}\NormalTok{(start)}
  \FunctionTok{put\_log}\NormalTok{(}\StringTok{"Function: \textasciigrave{}make\_source\_datasets\textasciigrave{}: }
\StringTok{Set of K{-}Fold Cross Validation datasets created: edx\_CV"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{str}\NormalTok{(edx\_CV)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## List of 5
##  $ :List of 4
##   ..$ train_set     :'data.frame':   7172311 obs. of  6 variables:
##   .. ..$ userId   : int [1:7172311] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:7172311] 122 185 292 329 356 362 364 370 420 466 ...
##   .. ..$ rating   : num [1:7172311] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:7172311] 838985046 838983525 838983421 838983392 838983653 838984885 838983707 838984596 838983834 838984679 ...
##   .. ..$ title    : chr [1:7172311] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Star Trek: Generations (1994)" ...
##   .. ..$ genres   : chr [1:7172311] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Drama|Sci-Fi" ...
##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
##   .. ..- attr(*, "dimnames")=List of 2
##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
##   .. .. ..$ : chr [1:10677] "122" "185" "292" "329" ...
##   ..$ train.sgr     : tibble [18,669,190 x 6] (S3: tbl_df/tbl/data.frame)
##   .. ..$ userId   : int [1:18669190] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:18669190] 122 122 185 185 292 292 292 292 316 316 ...
##   .. ..$ rating   : num [1:18669190] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:18669190] 838985046 838985046 838983525 838983525 838983421 838983421 838983421 838983421 838983392 838983392 ...
##   .. ..$ title    : chr [1:18669190] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
##   .. ..$ genres   : chr [1:18669190] "Comedy" "Romance" "Action" "Crime" ...
##   ..$ validation_set:'data.frame':   1827744 obs. of  6 variables:
##   .. ..$ userId   : int [1:1827744] 1 1 1 1 2 2 2 2 3 3 ...
##   .. ..$ movieId  : int [1:1827744] 316 355 377 588 260 376 648 1049 110 1252 ...
##   .. ..$ rating   : num [1:1827744] 5 5 5 5 5 3 2 3 4.5 4 ...
##   .. ..$ timestamp: int [1:1827744] 838983392 838984474 838983834 838983339 868244562 868245920 868244699 868245920 1136075500 1133571071 ...
##   .. ..$ title    : chr [1:1827744] "Stargate (1994)" "Flintstones, The (1994)" "Speed (1994)" "Aladdin (1992)" ...
##   .. ..$ genres   : chr [1:1827744] "Action|Adventure|Sci-Fi" "Children|Comedy|Fantasy" "Action|Romance|Thriller" "Adventure|Animation|Children|Comedy|Musical" ...
##  $ :List of 4
##   ..$ train_set     :'data.frame':   7172306 obs. of  6 variables:
##   .. ..$ userId   : int [1:7172306] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:7172306] 122 185 292 316 329 355 356 364 370 377 ...
##   .. ..$ rating   : num [1:7172306] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:7172306] 838985046 838983525 838983421 838983392 838983392 838984474 838983653 838983707 838984596 838983834 ...
##   .. ..$ title    : chr [1:7172306] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
##   .. ..$ genres   : chr [1:7172306] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
##   .. ..- attr(*, "dimnames")=List of 2
##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
##   ..$ train.sgr     : tibble [18,669,201 x 6] (S3: tbl_df/tbl/data.frame)
##   .. ..$ userId   : int [1:18669201] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:18669201] 122 122 185 185 185 292 292 316 316 329 ...
##   .. ..$ rating   : num [1:18669201] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:18669201] 838985046 838985046 838983525 838983525 838983525 838983421 838983421 838983392 838983392 838983392 ...
##   .. ..$ title    : chr [1:18669201] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
##   .. ..$ genres   : chr [1:18669201] "Comedy" "Romance" "Action" "Crime" ...
##   ..$ validation_set:'data.frame':   1827749 obs. of  6 variables:
##   .. ..$ userId   : int [1:1827749] 1 1 1 1 2 2 2 2 3 3 ...
##   .. ..$ movieId  : int [1:1827749] 362 520 539 594 539 590 733 1210 1252 1408 ...
##   .. ..$ rating   : num [1:1827749] 5 5 5 5 3 5 3 4 4 3.5 ...
##   .. ..$ timestamp: int [1:1827749] 838984885 838984679 838984068 838984679 868246262 868245608 868244562 868245644 1133571071 1133571145 ...
##   .. ..$ title    : chr [1:1827749] "Jungle Book, The (1994)" "Robin Hood: Men in Tights (1993)" "Sleepless in Seattle (1993)" "Snow White and the Seven Dwarfs (1937)" ...
##   .. ..$ genres   : chr [1:1827749] "Adventure|Children|Romance" "Comedy" "Comedy|Drama|Romance" "Animation|Children|Drama|Fantasy|Musical" ...
##  $ :List of 4
##   ..$ train_set     :'data.frame':   7172307 obs. of  6 variables:
##   .. ..$ userId   : int [1:7172307] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:7172307] 122 185 292 316 329 355 362 370 377 420 ...
##   .. ..$ rating   : num [1:7172307] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:7172307] 838985046 838983525 838983421 838983392 838983392 838984474 838984885 838984596 838983834 838983834 ...
##   .. ..$ title    : chr [1:7172307] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
##   .. ..$ genres   : chr [1:7172307] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
##   .. ..- attr(*, "dimnames")=List of 2
##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
##   ..$ train.sgr     : tibble [18,669,195 x 6] (S3: tbl_df/tbl/data.frame)
##   .. ..$ userId   : int [1:18669195] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:18669195] 122 122 185 185 185 292 292 292 316 329 ...
##   .. ..$ rating   : num [1:18669195] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:18669195] 838985046 838985046 838983525 838983525 838983525 838983421 838983421 838983421 838983392 838983392 ...
##   .. ..$ title    : chr [1:18669195] "Boomerang (1992)" "Boomerang (1992)" "Net, The (1995)" "Net, The (1995)" ...
##   .. ..$ genres   : chr [1:18669195] "Comedy" "Romance" "Action" "Crime" ...
##   ..$ validation_set:'data.frame':   1827748 obs. of  6 variables:
##   .. ..$ userId   : int [1:1827748] 1 1 1 1 2 2 2 2 3 3 ...
##   .. ..$ movieId  : int [1:1827748] 356 364 539 616 590 719 780 786 151 213 ...
##   .. ..$ rating   : num [1:1827748] 5 5 5 5 5 3 3 3 4.5 5 ...
##   .. ..$ timestamp: int [1:1827748] 838983653 838983707 838984068 838984941 868245608 868246191 868244698 868244562 1133571026 1136075789 ...
##   .. ..$ title    : chr [1:1827748] "Forrest Gump (1994)" "Lion King, The (1994)" "Sleepless in Seattle (1993)" "Aristocats, The (1970)" ...
##   .. ..$ genres   : chr [1:1827748] "Comedy|Drama|Romance|War" "Adventure|Animation|Children|Drama|Musical" "Comedy|Drama|Romance" "Animation|Children" ...
##  $ :List of 4
##   ..$ train_set     :'data.frame':   7172311 obs. of  6 variables:
##   .. ..$ userId   : int [1:7172311] 1 1 1 1 1 1 1 1 1 1 ...
##   .. ..$ movieId  : int [1:7172311] 122 185 292 316 329 355 356 362 364 370 ...
##   .. ..$ rating   : num [1:7172311] 5 5 5 5 5 5 5 5 5 5 ...
##   .. ..$ timestamp: int [1:7172311] 838985046 838983525 838983421 838983392 838983392 838984474 838983653 838984885 838983707 838984596 ...
##   .. ..$ title    : chr [1:7172311] "Boomerang (1992)" "Net, The (1995)" "Outbreak (1995)" "Stargate (1994)" ...
##   .. ..$ genres   : chr [1:7172311] "Comedy|Romance" "Action|Crime|Thriller" "Action|Drama|Sci-Fi|Thriller" "Action|Adventure|Sci-Fi" ...
##   ..$ train_mx      : num [1:69878, 1:10677] 5 NA NA NA NA NA NA NA NA NA ...
##   .. ..- attr(*, "dimnames")=List of 2
##   .. .. ..$ : chr [1:69878] "1" "2" "3" "4" ...
##   .. .. ..$ : chr [1:10677] "122" "185" "292" "316" ...
##   ..$ train.sgr     : tibble [18,669,192 x 6] (S3: tbl_df/tbl/data.frame)
##   .. ..$ userId   : int [1:18669192] 1 1 1 1 1 1 1 1 1 1 ...
